01-cleaning training and testing data

### 2019-02-07 journals/01-cleaning_training_and_testing_data.Rmd
added session info to journal 01
spelling check

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

@@

- correcting the study 173 labels
- adjustiing the bullet and barrel values for the unknowns
- renaming the match variable as samesource
- selecting the desired variables

@@

- selecting the desired variables
- renaming the bullet and land variables
- creating study and set variables
- recoding the bullet and land names

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

@@

- correcting the study 173 labels
- adjusting the bullet and barrel values for the unknowns
- renaming the match variable as samesource
- selecting the desired variables

@@

- selecting the desired variables
- renaming the bullet and land variables
- creating study and set variables
- re-coding the bullet and land names

@@

# Session Info

```{r}
sessionInfo()
```
